---
title: "Online Pre-Registration System"
author: "Marivic Amuan, Nicole De Luna, Reysha Marie Salinas BSIT 2-C"
date: "2024-04-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


load/Read the responses.

```{r eval=FALSE}
library(readr)
library(dplyr)
library(readxl)
library(ggplot2)

response <- read_excel ("response.xlsx")
View(response)
summary(response)
```

----------DEMOGRAPHICS--------------
Demographics: Gender 
```{r}
gender <- table(response$Gender)  
gender <- as.data.frame(gender)  #dataframe

gender  

ggplot(gender, aes(x = Var1, y = Freq)) +  
  geom_bar(stat = "identity") +  
  labs(title = "Distribution of Gender",  
       x = "Gender",
       y = "Frequency") +
  theme_classic() +
  scale_fill_manual(values = c("blue", "pink"))

  ggsave("gender_Demographics.png") 

 
```
Demographics:Age
```{r}
age <- table(response$Age)

age <- as.data.frame(age)
age

ggplot(age, aes(x = factor(Var1), y = Freq)) + 
  geom_bar(stat = "identity") + 
  labs(title = "Age of Respondent", x = "Age Group", y = "Frequency") 


   ggsave("age_Demographics.png") 
```
Demographics:School 
```{r}
library(dplyr)
library(ggplot2)  


schooldf <- data.frame(school = tolower(gsub("[ -]", "", response$School)))


schools_grouped <- schooldf %>%
  group_by(school) %>%   
  summarise(count = n()) %>%
  arrange(desc(count))


ggplot(school_counts, aes(x = factor(school), y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "School of Respondents", x = "School", y = "Frequency") +
  theme(axis.text.x = element_text(angle = 55, hjust = 1))

ggsave("school_Demographics.png", width = 20, height = 10) 
```
Demographics:Time
```{r}
time <-table(response$Timestamp)

time <- as.data.frame(time)

time$Var1 <- strptime(time$Var1, format = "%Y-%m-%d %H:%M:%S")  # Parse timestamps
time$Var1 <- format(time$Var1, format = "%b %d, %Y %H:%M") 

ggplot(time, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity") +  
  labs(title = "Frequency of Timestamps", x = "Timestamp", y = "Frequency") +
  theme(axis.text.x = element_text(angle =90, hjust = ,  size = 5)) 


  ggsave("timestamp_Demographics.png")  #SAVE PNG
  
```
Demographics:Department&course
```{r}
#clean data
response$DepartmentCourse <- tolower(gsub("[ -]", "", response$`Department&course`))

# Create data frame
department_df <- table(response$DepartmentCourse) %>%
  as.data.frame() %>%
  mutate(Department_Course = rownames(.))   


ggplot(department_df, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity") + 
  labs(title = "Frequency of Department and Course Combinations",
       x = "Department & Course",  
       y = "Frequency") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 5)) 

# Display the chart
 
ggsave("Department&course_Demographics.png")  

```
Demographics:Year&Section
```{r}
#update clean data 
response$YearSection <- tolower(gsub("[ -]", "", response$`Year&Section`))


yearSec_df <- table(response$YearSection) %>%
  as.data.frame() %>%
  mutate(Year_Section = rownames(.))  

ggplot(yearSec_df, aes(x = Var1, y = Freq)) +
  geom_bar(stat = "identity") +  
  labs(title = "Frequency of Year and Section Combinations",
       x = "Year & Section", 
       y = "Frequency") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 5)) 


  ggsave("Year&Section_Demographics.png")
```

----------DETERMINANT----------------
Create data frame for questions.
```{r}
#Create data frame for questions.
  questions_column <- response[, 10:39]
  write.csv(questions_column, file = "questions.csv")

```
--------Mean and Standard Deviation-----

Performance Expectancy
```{r}
# Read the data 
data <- read.csv("questions.csv")

columns <- data[, 1:4]  

# Calculate the mean and standard deviation

mean <-mean(performance)
stds <- sd(performance)

cat("Means :\n", mean)

#Means  Performance Expectancy
 #2.421569

cat("\nStandard Deviations:\n", stds)

#Standard Deviations /Performance Expectancy
# 0.05125617

```
Effort Expectancy
```{r}
# Read the data 
data <- read.csv("questions.csv")

columns <- data[, 5:8]  

# Calculate the mean and standard deviation 
performance <- colMeans(columns) 
stds <- apply(columns, 2, sd)  

mean <-mean(performance)
stds <- sd(performance)

cat("Means :\n", mean)

#Means for Effort Expectancy
 #2.514706


cat("\nStandard Deviations:\n", stds)

#Standard Deviations for Effort Expectancy
 #0.06862745

```
Attitude Toward Using Technology
```{r}
# Read the data 
data <- read.csv("questions.csv")

columns <- data[, 9:12]  

# Calculate the mean and standard deviation 
performance <- colMeans(columns) 
stds <- apply(columns, 2, sd)  

mean <-mean(performance)
stds <- sd(performance)

cat("Means:\n", mean)

#Means for Attitude Toward Using Technology
 # 2.473039


cat("\nStandard Deviations:\n", stds)

#Standard Deviations for Attitude Toward Using Technology
 #0.04411765
```
Social influence
```{r}

columns <- data[, 13:16]  

# Calculate the mean and standard deviation 
performance <- colMeans(columns) 
stds <- apply(columns, 2, sd)  

mean <-mean(performance)
stds <- sd(performance)

cat("Means:\n", mean)

#Means for Social influence
 #  2.54902


cat("\nStandard Deviations:\n", stds)

#Standard Deviations for Social influence
 #0.06252002
```
Facilitating Conditions
```{r}

columns <- data[, 17:20]  

# Calculate the mean and standard deviation 
performance <- colMeans(columns) 
stds <- apply(columns, 2, sd)  

mean <-mean(performance)
stds <- sd(performance)

cat("Means:\n", mean)

#Means for Facilitating Conditions
 #2.477941



cat("\nStandard Deviations:\n", stds)

#Standard Deviations for Facilitating Conditions
 #0.05023015
```
Self-Efficacy
```{r}

columns <- data[, 21:24]  

# Calculate the mean and standard deviation 
performance <- colMeans(columns) 
stds <- apply(columns, 2, sd)  

mean <-mean(performance)
stds <- sd(performance)

cat("Means:\n", mean)

#Means for Self-Efficacy
 # 2.544118


cat("\nStandard Deviations:\n", stds)

#Standard Deviations for Self-Efficacy
 #0.09214296
```
Anxiety
```{r}

columns <- data[, 25:28]  

# Calculate the mean and standard deviation 
performance <- colMeans(columns) 
stds <- apply(columns, 2, sd)  

mean <-mean(performance)
stds <- sd(performance)

cat("Means:\n", mean)

#Means for Anxiety
 # 2.632353


cat("\nStandard Deviations:\n", stds)

#Standard Deviations for Anxiety
 #0.0404226
```
Behavioral Intention to Use the System
```{r}

columns <- data[, 29:30]  

# Calculate the mean and standard deviation 
performance <- colMeans(columns) 
stds <- apply(columns, 2, sd)  

mean <-mean(performance)
stds <- sd(performance)

cat("Means:\n", mean)

#Means for Behavioral Intention to Use the System
 #  2.514706


cat("\nStandard Deviations:\n", stds)

#Standard Deviations for Behavioral Intention to Use the System
 # 0.02079726
```

MEAN and STANDARD DEVIATION of each CATEGORY
```{r}
#data frame to store the means and standard deviations
  datacategory <- data.frame(
  Category = c("Performance Expectancy", "Effort Expectancy", "Attitude Toward Using Technology",
                "Social Influence", "Facilitating Conditions", "Self-Efficacy",
                "Anxiety", "Behavioral Intention to Use the System"),
  Mean = c(2.421569, 2.514706, 2.473039, 2.54902, 2.477941, 2.544118, 2.632353, 2.514706),
  Standard_Deviation = c(0.05125617, 0.06862745, 0.04411765, 0.06252002, 0.05023015, 0.09214296, 0.0404226, 0.02079726)
)
  datacategory #view
  #save csv
 write.csv(datacategory, "categorymeanStandarddev.csv") 


library(ggplot2)

#bar plot with means and standard deviations
bar_plot <- ggplot(summary_data, aes(x = Construct, y = Mean)) +
  geom_bar(stat = "identity", fill = "green", alpha = 0.7) +
  geom_errorbar(aes(ymin = Mean - Standard_Deviation, ymax = Mean + Standard_Deviation), width = 0.4, color = "black", alpha = 0.7) +
  labs(title = "Means and Standard Deviations",
       x = "Category",
       y = "Rating Scale") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Print the bar plot
print(bar_plot)

ggsave("categoryMeansStd.png")
```
MEAN and STANDARD DEVIATION of each column
```{r}
# Read data from CSV file
data <- read.csv("questions.csv")

performance <- data[, 1:4]  # Performance Expectancy
effort <- data[, 5:8]        # Effort Expectancy
attitude <- data[, 9:12]     # Attitude Toward Using Technology
social <- data[, 13:16]      # Social Influence
facilitating <- data[, 17:20]# Facilitating Conditions
self <- data[, 21:24]       # Self-Efficacy
anxiety <- data[, 25:28]    # Anxiety
behavioral <- data[, 29:30] # Behavioral Intention to Use the System


calculate_summary <- function(category) {
  mean_values <- colMeans(category)
  std_values <- apply(category, 2, sd)
  return(data.frame(Category = colnames(category), Mean = mean_values, StandardDeviation = std_values))
}

#mean and standard deviation for each category
performance_summary <- calculate_summary(performance)
effort_summary <- calculate_summary(effort)
attitude_summary <- calculate_summary(attitude)
social_summary <- calculate_summary(social)
facilitating_summary <- calculate_summary(facilitating)
self_summary <- calculate_summary(self)
anxiety_summary <- calculate_summary(anxiety)
behavioral_summary <- calculate_summary(behavioral)

# summaries into one data frame
all_summaries <- rbind(performance_summary, effort_summary, attitude_summary, social_summary, facilitating_summary, self_summary, anxiety_summary, behavioral_summary)

#combined summary
print(all_summaries)

# mean and standard deviation for each category
for (category in unique(all_summaries$Category)) {
  category_data <- subset(all_summaries, Category == category)
  barplot(height = c(category_data$Mean, category_data$StandardDeviation), beside = TRUE, ylim = range(c(category_data$Mean, category_data$StandardDeviation)) * c(0.9, 1.1),
          names.arg = c("Mean", "Standard Deviation"),
          main = paste("Mean and Standard Deviation of", category),
          col = c("yellow", "orange"),
          xlab = ,
          ylab = ,
           cex.axis = 0.8,  
          cex.lab = 0.9,   
          cex.main = 0.6)
}

```

